---
title: "HSMR Main Report - {{publication_period}}"
author: "Automated HSMR Pipeline"
date: "{{generation_date}}"
output:
  html_document:
    toc: yes
    df_print: kable
  pdf_document: # Requires LaTeX
    toc: yes
# params:
#   publication_period: "YYYY QN" # Will be passed from knit script
#   generation_date: "YYYY-MM-DD"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# Load common libraries if needed by multiple chunks
# library(dplyr)
# library(ggplot2)
# library(readr)
# library(here)
# library(jsonlite)

# Access parameters passed from rmarkdown::render()
# These would be set based on hsmr_config.json by the knitting script
# For direct knitting, you can set them in a 'params' block above or interactively.
# publication_period <- ifelse(exists("params") && !is.null(params$publication_period), params$publication_period, "TEST YYYY QN")
# generation_date <- ifelse(exists("params") && !is.null(params$generation_date), params$generation_date, Sys.Date())

# config_data <- jsonlite::read_json(here::here("hsmr_config.json")) # Load config if needed directly
# smr_data_path <- here::here(config_data$output_paths$processed_data_dir, paste0("smr_output_", publication_period, ".csv"))
# trends_data_path <- here::here(config_data$output_paths$processed_data_dir, paste0("trends_output_", publication_period, ".csv"))
```

# Introduction

This report presents the Hospital Standardised Mortality Ratios (HSMR) for the period `r ifelse(exists("params") && !is.null(params$publication_period), params$publication_period, "YYYY QN")`.
This document was generated on `r ifelse(exists("params") && !is.null(params$generation_date), params$generation_date, Sys.Date())`.

## Section 1: SMR Data Summary (Placeholder)

```{r load_smr_data, include=FALSE}
# This chunk would load smr_output_...csv based on params or config
# For simulation, we create a dummy dataframe
smr_data_placeholder <- data.frame(
  Hospital = c("Hospital A", "Hospital B"),
  SMR_Value = c(1.05, 0.95),
  Patients = c(500, 600),
  Deaths = c(25, 20)
)
# In real Rmd:
# smr_data_df <- readr::read_csv(smr_data_path)
```

Below is a summary of the SMR data.
(More detailed tables and interpretations would go here).

```{r display_smr_table}
knitr::kable(smr_data_placeholder, caption = "Placeholder SMR Data Summary")
```

## Section 2: Trends Data Summary (Placeholder)

```{r load_trends_data, include=FALSE}
# This chunk would load trends_output_...csv
trends_data_placeholder <- data.frame(
  Time_Period = c("2023 Q1", "2023 Q2", "2023 Q3", "2023 Q4"),
  Crude_Mortality_Rate = c(0.05, 0.052, 0.049, 0.051)
)
# In real Rmd:
# trends_data_df <- readr::read_csv(trends_data_path)
```

Below is a summary of the trends data.
(More detailed tables, plots, and interpretations would go here).

```{r display_trends_table}
knitr::kable(trends_data_placeholder, caption = "Placeholder Trends Data Summary")
```

# Conclusion (Placeholder)

Further analysis and detailed findings are available in supplementary materials.

---
*This report was generated automatically.*
---
